### 2018-03-18 Sections/physical_architectures_for_quantum_computing.tex
tiny

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{quantum_walk_evolution}
\caption{Evolution on a 1D quantum walk on a line with a Hadamard coin operator. The walker begins localised at the origin and then spreads out as a superposition over the position space ($x$) with time ($t$). A key feature of this distribution is that its variance grows quadratically with time, compared with linear growth for the equivalent classical random walk. This enhanced spreading forms the basis of the quantum walk search algorithm, with quadratic enhancement compared to a classical search.} \label{fig:QW_ev}
\end{figure}

>>>>

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{quantum_walk_evolution}
\caption{Evolution on a 1D quantum walk on a line with a Hadamard coin operator. The walker begins localised at the origin and then spreads out as a superposition over the position space ($x$) with time ($t$). A key feature of this distribution is that its variance grows quadratically with time, compared with linear growth for the equivalent classical random walk. This enhanced spreading forms the basis of the quantum walk search algorithm, with quadratic enhancement compared to a classical search \cite{QWSearch}.} \label{fig:QW_ev}
\end{figure}
